Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\xavier{To see the impact of a faculae on the different parameters of the CCF, we simulated the effect of an equatorial faculae of size 3\% relative to the visible stellar hemisphere. The faculae is face on when the phase equals to 0. Note that a 3\% faculae is relatively big for the Sun. At maximum activity, big faculae have generally a size of 1\%.
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is slightly different with respect to the two others, with a maximum amplitude happening at a different phase.}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{center}
\end{figure}

>>>>

To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial faculae \jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} of size 3\% relative to the visible stellar hemisphere. The faculae is face on when the phase equals to 0. Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\%. \jessi{Is there a reference for this that could be added?}
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (RV \jessi{I believe this was going to be updated to ``N mean RV''?}), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase. SN mean RV seems to have the smallest spurious variations caused by the faculae.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{center}
\end{figure}
